\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}

% IPES 2026 Abstract — 500 words max
% Topic label: Money & Finance (or Other)

\begin{document}

\textbf{Who Pays, Who Punishes? Pandemic Wealth Shocks and Electoral Accountability Across Democracies}

\bigskip

Did the economic costs of the COVID-19 pandemic shape electoral accountability, and did the distribution of those costs across the wealth spectrum determine which incumbents were punished? We address this question using harmonized household wealth and income microdata from the Luxembourg Wealth Study (LWS) and Luxembourg Income Study (LIS), covering ten democracies that held elections during or shortly after the pandemic: the United States (2020), Canada (2021), the United Kingdom (2021), Japan (2021), South Korea (2022), Australia (2022), France (2022), Denmark (2022), Norway (2021), and Spain (2023).

Our empirical strategy proceeds in two stages. First, using LWS balance sheet data with pre-pandemic (2017--2019) and post-pandemic (2020--2023) waves, we measure how the pandemic redistributed wealth within each country. We decompose changes in household net worth by asset class---housing, equities, deposits, debt---and income quintile, identifying which segments of each country's wealth distribution bore the largest losses. We construct a country-level \textit{base exposure index} measuring the degree to which pandemic wealth shocks were concentrated among the incumbent party's electoral base. Countries where the incumbent's supporters were disproportionately exposed to wealth losses---through stock market declines, small business closures, or housing market disruptions---should exhibit stronger electoral accountability.

Second, we test whether cross-national variation in base exposure predicts the magnitude of anti-incumbent voting swings in pandemic-era elections. Using subnational election data (which we have assembled at the county, constituency, or precinct level for six of the ten countries), we estimate the within-country relationship between local wealth vulnerability and vote change, then pool estimates across countries to test whether the base-exposure mechanism generalizes.

Our identification strategy exploits the fact that pre-pandemic wealth composition---the share of household assets held in equities versus housing versus deposits---is structurally determined by each country's financial system (stock-market-based versus bank-based economies) and by long-run institutional factors that predate the pandemic. We use pre-pandemic asset composition interacted with the global pandemic shock (a shift-share design) to instrument for country-specific wealth losses, isolating the component of wealth change attributable to structural financial exposure rather than domestic policy responses.

Preliminary evidence from the United States supports this framework. Using individual-level data from the Cooperative Election Study and county-level election returns, we find that voters who experienced personal economic costs---particularly job loss and bereavement---were significantly more likely to defect from the incumbent, and this effect is concentrated among the incumbent's prior supporters. A shift-share instrumental variables analysis confirms the causal interpretation. The present paper extends this single-country finding to a comparative framework that leverages cross-national variation in financial structure and wealth inequality.

This paper contributes to the IPE literature on the domestic political consequences of economic shocks by showing that the \textit{distributional} incidence of crisis costs---not merely their aggregate magnitude---determines electoral accountability. The findings have implications for understanding how financial globalization, which shapes household asset portfolios and exposure to global shocks, conditions the political response to international crises.

\end{document}
